### 2013-07-03 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
adding write up for multiple set calculations

To motivate this problem, consider the square domain presented in
Figure~\ref{fig:ddmc_example} and on this domain we imagine a Monte
Carlo particle transport problem. If the domain were decomposed into 9
subdomains as shown, each of those subdomains and their associated
data (i.e. cross sections) could be owned by a different parallel
process in the computation. In Figure~\ref{fig:ddmc_example}, the
tracks of 3 particles that are born in the center subdomain are
shown. In this example, particle A is first transported from the
center domain to the domain directly to the left. Before the
scattering event in the new domain may be processed, particle A must
vbe communicated between between the two parallel processes that own
those domains. For any given particle in the transport simulation,
this communication event may hardly occur during the lifetime of the
particle (particle B), or may occur many times (particle C) depending
on the problem parameters and the random path in phase space taken by
the particle. Scalable parallel algorithms for domain decomposed Monte
Carlo are those that handle this domain-to-domain communication of
particles effectively and balance it with the on-process computations
for particle interactions, tallies, response calculations, and other
simulation requirements.
\begin{figure}[t!]
  \begin{center}
    \scalebox{1.5}{
      \input{chapters/parallel_mc/ddmc_example.pdftex_t} }
  \end{center}
  \caption{\textbf{Domain decomposed Monte Carlo transport example
      illustrating how domain decomposition requires parallel
      communication of particles.}}
  \label{fig:ddmc_example}
\end{figure}

@@

For strong scaling, the objective is to then decrease the runtime of a
fixed size global problem as a linear function of $P$. Based on this,
we can define the strong scaling \textit{absolute efficiency} as:
\begin{equation}
  \eta_{strong}(N,P) = \frac{1}{P} \frac{T(N,1)}{T(N,P)}\:,
  \label{eq:strong_scaling_absolute}
\end{equation}
where $T(N,P)$ is the wall time for a computation of global size $N$
using $P$ processes. Note here that this particular definition is
measured with respect to a serial computation. On leadership class
machines, it is often the case that a problem size large enough to
effectively execute on $O(10,000)$ cores or larger is significantly
larger than any problem that may be solved by a single core due to
memory restrictions. Therefore, we consider absolute scaling for a
base case where $Q$ processes are used instead of a serial
computation:
\begin{equation}
  \eta_{strong}(N,P|Q) = \frac{Q}{P} \frac{T(N,Q)}{T(N,P)}\:.
  \label{eq:strong_scaling_absolute_ref}
\end{equation}
The absolute efficiency measure presented here only considers the
total time to solution. Often, that total time to solution may be
changing for an iterative method due to the fact that the number of
iterations required to converge may be changing as a function of
$P$. This will often happen in cases where modifying $N$ changes the
spectral character of the problem, often making it stiffer and
therefore more difficult to solve when $N$ increases. Therefore we
also consider \textit{algorithmic efficiency} from Keyes' work which
considers this potential change in iteration count:
\begin{equation}
  \eta_{alg}(N,P|Q) = \frac{I(N,Q)}{I(N,P)}\:,
  \label{eq:algorithmic_efficiency}
\end{equation}
where $I(N,P)$ is the number of iterations required to converge a
problem of global size $N$ computed using $P$ processes. We can then
adjust the absolute efficiency using this new algorithmic efficiency
in order to compute the parallel scalability of a single iteration
such that algorithmic effects may be neglected. We define the
\textit{implementation efficiency} as:
\begin{equation}
  \eta_{impl}(N,P|Q) = \frac{\eta}{\eta_{alg}}\:,
  \label{eq:implementation efficiency}
\end{equation}
using the absolute efficiency in the numerator, giving an effective
measure of scalability of a single iteration of the algorithm.

@@

For each parallel performance metric presented in the previous
section, a reference case is required to compute efficiencies for all
other cases. For smaller machines, often a serial computation can be
performed and used as the base case to get a true measure of speed-up
for a particular problem. For our scaling studies, we will always use
as a reference case a calculation which uses 16 cores, filling an
entire node of the machine. We fill an entire node so that we may
ignore the effects on scalibility measures that arise from using only
a subset of cores in a node. Typically this results in a large drop in
efficiency from a serial computation to a calculation that fills the
entire node. Once a node is filled, adding subsequent nodes has less
of an effect on the scaling, providing a more stable region of
analysis.

@@

\subsubsection{Strong Scaling}
\label{subsubsec:overlapping_strong}

\subsubsection{Weak Scaling}
\label{subsubsec:overlapping_weak}

@@

\subsubsection{Strong Scaling}
\label{subsubsec:msod_strong}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_ms_time.pdf}
  \end{center}
  \caption{\textbf{Wall time in seconds to solution for each case.}}
  \label{fig:titan_strong_ms_time}
\end{figure}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{c}{Case}& 
      \multicolumn{1}{c}{Iterations}&
      \multicolumn{1}{c}{$\eta_{alg}$} \\\hline
      1 & 22 & 1.0 \\
      2-split & 22 & 1.0 \\
      2-replicated & 16 & 1.375 \\
      4-split & 22 & 1.0 \\
      4-replicated & 13 & 1.692 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Strong scaling algorithmic efficiency using
      multiple sets.}}
  \label{tab:ms_strong_alg_eff}
\end{table}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_ms_impeff.pdf}
  \end{center}
  \caption{\textbf{Strong scaling implementation efficiency relative
      to 16-core 1-set base case.}}
  \label{fig:titan_strong_ms_impeff}
\end{figure}

\subsubsection{Weak Scaling}
\label{subsubsec:msod_weak}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_ms_time.pdf}
  \end{center}
  \caption{\textbf{Wall time in seconds to solution for each case.}}
  \label{fig:titan_weak_ms_time}
\end{figure}

For a multiple set analysis of the weak scaling results, we have to
consider that adding sets to the problem is actually a form of strong
scaling. Consider a single set problem ($S=1$) for a given $P$ and
$N$. When that problem is now solved using 2 sets we have $S=2$, $N$
and $2P$. For any number of sets we then have a global problem size of
$N$ while the number of processors is $SP$ where $P$ is the number of
processors in the single set case. Therefore, $N/P$ is no longer fixed
in the weak scaling study but rather $N/(SP)$ is fixed. Therefore, we
modify the weak scaling absolute efficiency relationship to account
for this fact:
\begin{equation}
\eta_{weak}(M|N,P|Q,S) = \frac{T(M,Q)}{S \times T(N,P)}\:,
  \label{eq:ms_weak_efficiency}
\end{equation}
where now the absolute efficiency is a function of the number of sets
in the problem. For problems where adding sets improves time to
solution, this new weak scaling formulation accounts for how
efficiently those extra resources are incorporated into the
problem. Without such a modification, the largest case run for the
split 4 set case would have a computed weak scaling efficiency of
nearly 100\% using the standard formula for absolute
efficiency. However, using 4 times as many cores as the single set
case increases the runtime for a fixed global problem size and
therefore we actually expect to compute a very low efficiency that
shows this very poor use of resources.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{c}{Case}& 
      \multicolumn{1}{c}{Iterations}&
      \multicolumn{1}{c}{$\eta_{alg}$} \\\hline
      1 & 22 & 1.0 \\
      2-split & 22 & 1.0 \\
      2-replicated & 16 & 1.375 \\
      4-split & 22 & 1.0 \\
      4-replicated & 13 & 1.692 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Weak scaling algorithmic efficiency using multiple
      sets.}}
  \label{tab:ms_weak_alg_eff}
\end{table}

@@

\subsubsection{Strong Scaling}
\label{subsubsec:full_clip_strong}

\subsubsection{Weak Scaling}
\label{subsubsec:full_clip_weak}

>>>>

To motivate this problem, consider the square domain presented in
Figure~\ref{fig:ddmc_example} and on this domain we imagine a Monte
Carlo particle transport problem. If the domain were decomposed into 9
subdomains as shown, each of those subdomains and their associated
data (i.e. cross sections) could be owned by a different parallel
process in the computation. In Figure~\ref{fig:ddmc_example}, the
tracks of 3 particles that are born in the center subdomain are
shown. In this example, particle A is first transported from the
center domain to the domain directly to the left. Before the
scattering event in the new domain may be processed, particle A must
be communicated between between the two parallel processes that own
those domains. For any given particle in the transport simulation,
this communication event may hardly occur during the lifetime of the
particle (particle B), or may occur many times (particle C) depending
on the problem parameters and the random path in phase space taken by
the particle. Scalable parallel algorithms for domain decomposed Monte
Carlo are those that handle this domain-to-domain communication of
particles effectively and balance it with the on-process computations
for particle interactions, tallies, response calculations, and other
simulation requirements.
\begin{figure}[t!]
  \begin{center}
    \scalebox{1.5}{
      \input{chapters/parallel_mc/ddmc_example.pdftex_t} }
  \end{center}
  \caption{\textbf{Domain decomposed Monte Carlo transport example
      illustrating how domain decomposition requires parallel
      communication of particles.}}
  \label{fig:ddmc_example}
\end{figure}

@@

For strong scaling, the objective is to then decrease the runtime of a
fixed size global problem as a linear function of $P$. Based on this,
we can define the strong scaling \textit{absolute efficiency} as:
\begin{equation}
  \eta_{strong}(N,P) = \frac{1}{P} \frac{T(N,1)}{T(N,P)}\:,
  \label{eq:strong_scaling_absolute}
\end{equation}
where $T(N,P)$ is the wall time for a computation of global size $N$
using $P$ processes. Note here that this particular definition is
measured with respect to a serial computation. On leadership class
machines, it is often the case that a problem size large enough to
effectively execute on $O(10,000)$ cores or larger is significantly
larger than any problem that may be solved by a single core due to
memory restrictions. Therefore, we consider absolute scaling for a
base case where $Q$ processes are used instead of a serial
computation:
\begin{equation}
  \eta_{strong}(N,P|Q) = \frac{Q}{P} \frac{T(N,Q)}{T(N,P)}\:.
  \label{eq:strong_scaling_absolute_ref}
\end{equation}
The absolute efficiency measure presented here only considers the
total time to solution. Often, that total time to solution may be
changing for an iterative method due to the fact that the number of
iterations required to converge may be changing as a function of
$P$. This will often happen in cases where modifying $N$ changes the
spectral character of the problem, often making it stiffer and
therefore more difficult to solve when $N$ increases. Therefore we
also consider \textit{algorithmic efficiency} from Keyes' work which
considers this potential change in iteration count:
\begin{equation}
  \eta_{alg}(N,P|Q) = \frac{I(N,Q)}{I(N,P)}\:,
  \label{eq:algorithmic_efficiency}
\end{equation}
where $I(N,P)$ is the number of iterations required to converge a
problem of global size $N$ computed using $P$ processes. We can then
adjust the absolute efficiency using this new algorithmic efficiency
in order to compute the parallel scalability of a single iteration
such that algorithmic effects may be neglected. We define the
\textit{implementation efficiency} as:
\begin{equation}
  \eta_{impl}(N,P|Q) = \frac{\eta}{\eta_{alg}}\:,
  \label{eq:implementation_efficiency}
\end{equation}
using the absolute efficiency in the numerator, giving an effective
measure of scalability of a single iteration of the algorithm.

@@

For each parallel performance metric presented in the previous
section, a reference case is required to compute efficiencies for all
other cases. For smaller machines, often a serial computation can be
performed and used as the base case to get a true measure of speed-up
for a particular problem. For our scaling studies, we will always use
as a reference case a calculation which uses 16 cores, filling an
entire node of the machine. We fill an entire node so that we may
ignore the effects on scalability measures that arise from using only
a subset of cores in a node. Typically this results in a large drop in
efficiency from a serial computation to a calculation that fills the
entire node. Once a node is filled, adding subsequent nodes has less
of an effect on the scaling, providing a more stable region of
analysis.

@@

@@

Given that overlap was not successful in boosting parallel
efficiencies, we next look to apply replication to the problem in the
form of multiple sets. Before performing parallel scaling studies
using multiple sets, several aspects of the replicated parallel
problem must be considered in order to effectively craft the studies
and interpret their results. First is the question of how many
stochastic histories to use to generate the correction vector in the
MCSA iteration. For this work we consider two choices, the split case
and the fully replicated case. As an example, consider a single set
problem where 20,000 histories are used in the Monte Carlo solve. If
we choose the split case, then solving the same problem with 2 sets
would give 10,000 histories in each set and 4 sets would give 5,000
histories in each set. Splitting the histories in this way provides
the same global number of histories used to compute the correction in
the single set problem. We expect to reduce the time to solution by
doing this as each individual set solve will occur faster in an almost
linear fashion with the reduced number of histories. For the
replicated history case, each additional set in the problem will use
just as many histories as the single set case. Using 2 sets with fully
replicated histories for our example problem then has each set
computing 20,000 histories with 40,000 global histories in the
computation. For the 4 set case, the number of global histories is
increased to 80,000. We also expect this type of replication to reduce
the time to solution as the extra global histories should reduce the
stochastic uncertainty in the correction vector and reduce the overall
number of MCSA iterations required to converge.

For the strong scaling study, we apply the additional sets as
follows. Using the same problems as the pure domain decomposition
scaling study, the multiple sets are used to replicate those problems
and boost the core count. For example, for the 4 set case, the data
point at 64 cores has the same $N/P$ ratio as the single set problem
with 16 cores. This is due to the fact that $N$ is fixed for the
strong scaling study and 4 replications gives a set size of 16
cores. For the 2 set case, the 32 core data point is solving the same
$N/P$ problem as the 16 core base case. In addition to considering the
replicated domain, we must also consider how to modify the
efficiencies we will compute. For the strong scaling case, recall that
the objective is to decrease the time to solution for a given global
problem size $N$ by increasing $P$. Therefore, we may use
Eqs~(\ref{eq:strong_scaling_absolute_ref}),
(\ref{eq:algorithmic_efficiency}), and
(\ref{eq:implementation_efficiency}) to compute the various strong
scaling efficiencies, but we must modify the reference computation in
each of these formulas to reflect our objective. For all efficiency
computations, the 16 core single set computation will be used as the
reference case. By adding more cores to the problem, either by
replicating with multiple sets, or decreasing the local problem size,
any computational resources added to the problem should aim to result
in speedup. If this speedup for one technique is less than another,
then that technique is deemed a less efficient use of those
computational resources.

For the multiple sets problem, the single set strong scaling study
from the pure domain decomposition base case was repeated for multiple
sets with both splitting of histories across sets and full replication
of histories across sets. Figure~\ref{fig:titan_strong_ms_time} gives
the actual wall times for these computations. There are two important
features to note in the wall time data. First, splitting the histories
amongst sets instead of replicating them is faster due to the fact
that cutting the number of histories in half reduces the time of an
iteration by a factor that is nearly linear while increasing linearly
the number of histories through replication does not decrease the
iterations required to converge by a linear factor. Second, until the
strong scaling wall is hit starting at around 10,000 cores, the single
set case actually perfoms the fastest with only marginal improvement in
runtimes at higher numbers of cores with more sets. At these larger
numbers of cores, however, the improvements are so modest that one is
better off running the same problem using a single set at lower core
counts to conserve computational resource while maintaining a good tim
to solution.

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_ms_time.pdf}
  \end{center}
  \caption{\textbf{Wall time in seconds to solution for each case for
      the strong scaling study with multiple sets.}}
  \label{fig:titan_strong_ms_time}
\end{figure}

From this timing data we then compute the absolute efficiencies for
strong scaling as given in Figure~\ref{fig:titan_strong_ms_eff}. As
observed in the timing data, because the single set case had the
fastest run times up to the strong scaling wall it also has the best
observed efficiencies. For the 2 set case with history splitting,
although the time to perform an iteration was nearly cut in half, the
extra parallel overhead associated with reducing the tally across the
blocks to combine the set results increases run times and reduces
efficiencies.This reduction across blocks is even more obvious for the
4 set case. For the replicated cases, we do observe a flat region of
parallel efficiencies at larger core counts (around 32,000 for the 4
set case with history replication), but the additional cores do not
reduce the runtime of the global problem efficiently. Ultimately, all
cases effectively hit the strong scaling wall at the same time. We
expect this if we consider the fact that adding sets to the problem is
in itself effectively a form of strong scaling. For any given problem
of fixed size $N$, adding extra sets to the computation decreases the
ratio of $N/P$ as $P$ will grow with the addition of sets. For the
split history case, the splitting further exacerbates this situation
by further decreasing the amount of histories that will be computed in
the local domain, giving a larger ratio of communication to work in
the Monte Carlo solve. As with with single set results, we also
observe some efficiencies greater than unity for the multiple set
cases also due to improved cache utilization.

@@

Also of interest here is the effect of splitting histories amongst
sets versus replicating them on the iterative performance of the
method. Table~\ref{tab:ms_strong_alg_eff} gives the iterations
required to converge and computed algorithmic efficiences for each of
the cases presented in the scaling data. As expected, splitting
histories maintains a fixed global number of histories and therefore
maintained the number of iterations required to converge relative to
the single set base case. When histories were replicated, adding sets
decreased the number of iterations required to converge in a nonlinear
fashion. Using these algorithmic efficiencies, the implementation
efficiencies for the multiple set cases were computed and are given in
Figure~\ref{fig:titan_strong_ms_impeff}. From these results, we see
that the replicated history cases are even less efficient than in the
absolute case. Not only do we have the additional parallel overhead of
doing the block level reduction, but we also have additional histories
that increase the time to solution for a single iteration. Given that
the time to solution is not efficiently improved using multiple sets
in both the split and replicated history cases, multiple set domain
decomposition is not an effective means to boost the strong scaling
efficiencies of MCSA.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Case}& 
      \multicolumn{1}{c}{Iterations}&
      \multicolumn{1}{c}{$\eta_{alg}$} \\\hline
      1 & 22 & 1.0 \\
      2-split & 22 & 1.0 \\
      2-replicated & 16 & 1.375 \\
      4-split & 22 & 1.0 \\
      4-replicated & 13 & 1.692 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Strong scaling algorithmic efficiency using
      multiple sets.}}
  \label{tab:ms_strong_alg_eff}
\end{table}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_strong_ms_impeff.pdf}
  \end{center}
  \caption{\textbf{Strong scaling implementation efficiency relative
      to the 16-core 1-set base case.}}
  \label{fig:titan_strong_ms_impeff}
\end{figure}

Next, we continue to a weak scaling study of the multiple sets
problem. As with the strong scaling study, we will modify the pure
domain decomposition study to account for the additional
replication. For each calculation in the single set study, that
problem will be replicated either 2 or 4 times with both split and
replicated histories to assess the effects on scalability and
runtime. Figure~\ref{fig:titan_weak_ms_time} gives the wall times from
the multiple sets weak scaling study. Of primary importance here is
the fact that adding sets to the problem with both split and
replicated histories actually decreases the time to solution. This was
not observed in the strong scaling case due to the larger decrease in
computational work as the number of cores was increased. This result
is significant in that it shows a solution technique in which the
linear problem can actually be replicated and enhance time to
solution, something that cannot be acheived with conventional
methods. At larger core counts, however, this reduction in compute
time is not as great as at lower core counts due to the fact that the
tally reduction across blocks requires more resources. In addition, at
over 130,000 cores for the largest 4 set computation, load balance is
likely becoming an issue due to the linear system and subsequent
parallel matrix and vector operations only occuring on a subset of the
entire processor space of the problem.

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/parallel_mc/titan_weak_ms_time.pdf}
  \end{center}
  \caption{\textbf{Wall time in seconds to solution for each case for
      the weak scaling study with multiple sets.}}
  \label{fig:titan_weak_ms_time}
\end{figure}

For a multiple set analysis of the weak scaling timing results, we
again have to consider that adding sets to the problem is actually a
form of strong scaling. Consider a single set problem ($S=1$) for a
given $P$ and $N$. When that problem is now solved using 2 sets we
have $S=2$, $N$ and $2P$. For any number of sets we then have a global
problem size of $N$ while the number of processors is $SP$ where $P$
is the number of processors in the single set case. Therefore, $N/P$
is no longer fixed in the weak scaling study but rather $N/(SP)$ is
fixed. As a result, we modify the weak scaling absolute efficiency
relationship to account for this fact:
\begin{equation}
\eta_{weak}(M|N,P|Q,S) = \frac{T(M,Q)}{S \times T(N,P)}\:,
  \label{eq:ms_weak_efficiency}
\end{equation}
where now the absolute efficiency is a function of the number of sets
in the problem. Interestingly, Eq~(\ref{eq:ms_weak_efficiency}) has a
very similar form to the strong scaling efficiency given by
Eq~(\ref{eq:strong_scaling_absolute}), representative of the strong
scaling nature of adding additional sets. For problems where adding
sets improves time to solution, this new weak scaling formulation
accounts for how efficiently those extra resources are incorporated
into the problem. Without such a modification, the largest case run
for the split 4 set case would have a computed weak scaling efficiency
of nearly 100\% using the standard formula for absolute
efficiency. However, using 4 times as many cores as the single set
case increases the runtime for a fixed global problem size and
therefore we actually expect to compute a very low efficiency that
shows this very poor use of resources.

Figure~\ref{fig:titan_weak_ms_eff} gives the results of the weak
scaling efficiencies using the multiple set metric given by
Eq~(\ref{eq:ms_weak_efficiency}). Although we do reduce the time to
solution over the base cases for nearly all data points, the
observation here is that the reduction in time to solution is still
not large enough to efficiently use all resources. For example, for
the 2 set case to be a perfect use of resources with either split or
replicated histories, the runtime of that calculation must be half of
that for the single set case. For the 4 set case, this run time should
be a quarter of the single set case for perfect scaling. This was not
the observation for the runtimes in
Figure~\ref{fig:titan_weak_ms_time} and therefore the single set case
is still the most efficient use of computational resources in this
scaling study.

@@

As in the strong scaling case, splitting and replicating histories
across sets had effectively the same results for the weak scaling
study with the iterations to converge and compute algorithmic
efficienies given by Table~\ref{tab:ms_weak_alg_eff}. Again, when the
implementation efficiencies are computed, we see in
Figure~\ref{fig:titan_weak_ms_impeff} that splitting histories amongst
sets is still a more efficient manner of introducing multiple sets
rather than replicating histories in an attempt to reduce the number
of iterations required to converge.  Here we also note that this is
not a true weak scaling study as indicated by
Eq~(\ref{eq:ms_weak_efficiency}) but rather an odd combination of both
weak and strong scaling. Regardless of this, although multiple sets
are not the most efficient use of resources in this analysis, they do
enhance the time to solution through replication and do so
significantly at core counts of O(1,000) and lower. In both the weak
and strong scaling cases, due to the additional computational and
communication overhead of adding sets to the system, one should never
expect to boost parallel efficiencies for MCSA using this
technique. Further, in a purely strong scaling environment, no
performance gains should be expected as adding sets creates an even
more parasitic ratio of $N/P$. In a weak scaling environment, although
no efficiency increase will be noted, one can expect an enhancement of
time to convergence by replicating.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lcc}\hline\hline
      \multicolumn{1}{l}{Case}& 
      \multicolumn{1}{c}{Iterations}&
      \multicolumn{1}{c}{$\eta_{alg}$} \\\hline
      1 & 22 & 1.0 \\
      2-split & 22 & 1.0 \\
      2-replicated & 16 & 1.375 \\
      4-split & 22 & 1.0 \\
      4-replicated & 13 & 1.692 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Weak scaling algorithmic efficiency using multiple
      sets.}}
  \label{tab:ms_weak_alg_eff}
\end{table}

@@
